|

### 2019-01-03 Paper 2019.Rmd
Getting summaries printed, with thanks to Matt Worthington

```{r setup, include=FALSE}
# This is all necessary setup stuff, including packages and for Markdown
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(texreg) # For regression outputs #fail 
library(kableExtra) # For regression outputs 
library(broom) # Because Matt Worthington said so 
library(knitr) # Because Matt Worthington said so 
library(summarytools) # For summary statistics 
library(psych) # Also for summary statistics
```

@@

#### Insert Barber Summary Statistics Here. 
```{r Barber summary, eval=F}
# This is a summary it, but includes all the 99999s and doesn't have skew in it. 
stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

@@

# How about correlations? Unclear what this shows us. 
pairs(BarberNAs[3:6])

# This is a summary table for all the non-99999 values. 
stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
# How do I get this printed?

# An alternative, perhaps to combine if I can figure out how to print: 
# psych::describe(subset(BarberNAs[,3:6]))
```

@@

#### Insert CRI and CCI Summary Statistics Here  
```{r CRI summary, eval=F}
stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="text", digits=2, title="Descriptive Statistics of Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"))

@@

```{r Hausman test for CRI with campaign finance variables, eval=F}
phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
```

@@

```{r CRI output to table}
stargazer(cri.base.pooled, 
          cri.limits.pooled, 
          cri.limits.fixed,
          cri.limits.fixed.time, 
          type="text",
          title = "Table 2: Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
          out="collateral/CRI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          ) 
```

@@

##Results 
### Modeling campaign limits and corruption arrests 
*(rework based on which tables you'll show)*
The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

@@

@@

## Appendix A: Initital modeling of independent and dependent variables

*Clean up*
```{r output of initial correlations, results="asis", eval=T}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
  type="latex",
  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way")),
  font.size = "small",
  header = FALSE,
  column.sep.width = "-5pt",
  digits = 2, digits.extra = 0,
  no.space = TRUE, 
  omit.stat = "f"
  )
```
\elandscape

@@

#### Include Descriptive Statistics Here
```{r Alt and Lassen summary, eval=F}
stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])), type="text", digits=2, title="Descriptive Statistics of Control Variables", covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"))
```

>>>>

```{r setup, include=FALSE}
# This is all necessary setup stuff, including packages and for Markdown
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library (MASS) # For binomial regression 
library(pglm) # For panel + binomial 
# library(psych) # Also for summary statistics
# library(texreg) # For regression outputs #fail 
# library(kableExtra) # For regression outputs 
# library(broom) # Because Matt Worthington said so 
# library(summarytools) # For summary statistics 
```

@@

```{r Barber summary, eval=T}
# This is a summary it, but includes all the 99999s and doesn't have skew in it. 
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

@@

# How about correlations? Unclear what this shows us. 
# pairs(BarberNAs[3:6])

# An alternative, perhaps to combine if I can figure out how to print: 
# psych::describe(subset(BarberNAs[,3:6]))

# This is a summary table for all the state-years where limits exist:  
# stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
```

```{r Barber summary statistics fail, results="asis", eval=TRUE}
# This is what fails to knit (see error below)
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F)
```

@@

```{r CRI summary, results="asis", eval=T}
stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)

@@

```{r Hausman test for CRI with campaign finance variables}
phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
```

@@

```{r Empty, Binomial, and Poisson models}
# First, trying to run the model above but with the pglm() package
# pglm(formula, data, subset, na.action, effect = c("individual", "time", "twoways"), model = c("random", "pooling", "within", "between"), family, other = NULL, index = NULL, start = NULL, R = 20, ...)

# Initial correlations of independent variables with CCI 
pglm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, model = "within", index = c("st","year"), effect = "twoways", family = gaussian) 
# Return code 100: Initial value out of range. May have something to do with the interaction terms, because when I strip those out, the model at least returns something.

# What about Cale's empty model? 
cci.empty.pooling <- plm(CCI ~ st + year,
                   data = AltBarber, 
                   model="pooling")
summary(cci.empty.pooling)

cci.empty.within <- plm(CCI ~ st + year,
                   data = AltBarber, 
                   model="within")
summary(cci.empty.within)

# Verifying that I didn't screw up by not having st and year as variables in my preivous model 
cci.base.fixed.time.redo <- plm(CCI ~ st + year 
                   + jdiv  # Divided government
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within", 
                   effect = "twoways")
# stargazer(cci.base.fixed.time, cci.base.fixed.time.redo, type="text")
```

@@

##Results 
### Modeling campaign limits and corruption arrests 
The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

@@

```{r CCI output to table latex, results="asis", eval=T}
# Maaaaaybe figure out how to add back in those $ signs. 
stargazer(cci.base.pooled, 
          cci.limits.pooled, 
          cci.limits.fixed,
          cci.limits.fixed.time, 
          type="latex",
          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
  add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),     
  header=FALSE, 
  font.size = "small",
  # column.sep.width = "-5pt",
  digits = 2, digits.extra = 0,
  no.space = TRUE,
  omit.stat = "f"
  )

```{r CRI output to table latex, results="asis", eval=T}
stargazer(cri.base.pooled, 
          cri.limits.pooled, 
          cri.limits.fixed,
          cri.limits.fixed.time, 
          type="latex",
          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),
  header=FALSE, 
  font.size = "small",
  # column.sep.width = "-5pt",
  digits = 2, digits.extra = 0,
  no.space = TRUE,
  omit.stat = "f"
  )
```

@@

## Appendix A: Initital modeling of independent and dependent variables
```{r output of initial correlations, results="asis", eval=T}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits correlated with corruption convictions or reflections?",
  type="latex",
  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way")),
  font.size = "small",
  header = FALSE,
  column.sep.width = "-5pt",
  digits = 2, digits.extra = 0,
  no.space = TRUE, 
  omit.stat = "f"
  )
```
\elandscape

@@

```{r Alt and Lassen summary, results="asis", eval=T}
stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])), 
          type="latex", 
          digits=2, 
          title="Descriptive Statistics of Control Variables", 
          covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          header=FALSE,
          font.size = "small",
          column.sep.width = "-5pt",
          # digits = 2, digits.extra = 0,
          no.space = TRUE) 
```
